PRFDN: Reparameterize and Prune Disentangled U-Net for Efficient Image Super-resolution

### 2023-04-06 NTIRE 2023 RTSR Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)
修复

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{bm}

@@

\begin{table}[htbp]
    \resizebox{\columnwidth}{!}
    {
        \begin{tabular}{|c|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \bigstrut\\
    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \bigstrut\\
        \hline
        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 \bigstrut[t]\\
        SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
        FSRCNN[6] &       & 13K   & 37.00/0.9558 & 32.63/0.9088 & 31.53/0.8920 & 29.88/0.9020 & 36.67/0.9710 \\
        VDSR[19][13] &       & 666K  & 37.53/0.9587 & 33.03/0.9124 & 31.90/0.8960 & 30.76/0.9140 & 37.22/0.9750 \\
        DRCN[32][14] &       & 1774K & 37.63/0.9588 & 33.04/0.9118 & 31.85/0.8942 & 30.75/0.9133 & 37.55/0.9732 \\
        DRRN[30] &       & 298K  & 37.74/0.9591 & 33.23/0.9136 & 32.05/0.8973 & 31.23/0.9188 & 37.88/0.9749 \\
        MemNet[35] &       & 678K  & 37.78/0.9597 & 33.28/0.9142 & 32.08/0.8978 & 31.31/0.9195 & 37.72/0.9740 \\
        IDN[12] &       & 553K  & 37.83/0.9600 & 33.30/0.9148 & 32.08/0.8985 & 31.27/0.9196 & 38.01/0.9749 \\
        SRMDNF[42] &       & 1511K & 37.79/0.9601 & 33.32/0.9159 & 32.05/0.8985 & 31.33/0.9204 & 38.07/0.9761 \\
        CARN[1] &       & 1592K & 37.76/0.9590 & 33.52/0.9166 & 32.09/0.8978 & 31.92/0.9256 & 38.36/0.9765 \\
        LAPAR-A[18] &       & 548k  & 38.01/0.9605 & 33.62/0.9183 & 32.19/0.8999 & 32.10/0.9283 & 38.67/0.9772 \\
        IMDN[11] &       & 694K  & 38.00/0.9605 & 33.63/0.9177 & 32.19/0.8996 & 32.17/0.9283 & 38.88/0.9774 \\
        RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 \bigstrut[b]\\
        \hline
        \end{tabular}%
    }
\end{table}%

\subsection{Discussion}
Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency. On both the DIV2K and LSDIR datasets, our method achieved high PSNR and SSIM scores, indicating that our approach can greatly improve image resolution while preserving image features and textures.

Additionally,when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{bm}
\usepackage{multirow}
\usepackage{multicol}

@@

\begin{table}[htbp]
    \resizebox{\columnwidth}{!}
    {
        \begin{tabular}{|c|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \\
    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \\
        \hline
        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 [t]\\
        SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
        FSRCNN[6] &       & 13K   & 37.00/0.9558 & 32.63/0.9088 & 31.53/0.8920 & 29.88/0.9020 & 36.67/0.9710 \\
        VDSR[19][13] &       & 666K  & 37.53/0.9587 & 33.03/0.9124 & 31.90/0.8960 & 30.76/0.9140 & 37.22/0.9750 \\
        DRCN[32][14] &       & 1774K & 37.63/0.9588 & 33.04/0.9118 & 31.85/0.8942 & 30.75/0.9133 & 37.55/0.9732 \\
        DRRN[30] &       & 298K  & 37.74/0.9591 & 33.23/0.9136 & 32.05/0.8973 & 31.23/0.9188 & 37.88/0.9749 \\
        MemNet[35] &       & 678K  & 37.78/0.9597 & 33.28/0.9142 & 32.08/0.8978 & 31.31/0.9195 & 37.72/0.9740 \\
        IDN[12] &       & 553K  & 37.83/0.9600 & 33.30/0.9148 & 32.08/0.8985 & 31.27/0.9196 & 38.01/0.9749 \\
        SRMDNF[42] &       & 1511K & 37.79/0.9601 & 33.32/0.9159 & 32.05/0.8985 & 31.33/0.9204 & 38.07/0.9761 \\
        CARN[1] &       & 1592K & 37.76/0.9590 & 33.52/0.9166 & 32.09/0.8978 & 31.92/0.9256 & 38.36/0.9765 \\
        LAPAR-A[18] &       & 548k  & 38.01/0.9605 & 33.62/0.9183 & 32.19/0.8999 & 32.10/0.9283 & 38.67/0.9772 \\
        IMDN[11] &       & 694K  & 38.00/0.9605 & 33.63/0.9177 & 32.19/0.8996 & 32.17/0.9283 & 38.88/0.9774 \\
        RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 [b]\\
        \hline
        \end{tabular}%
    }
\end{table}%

\subsection{Conclusion}
Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency. On both the DIV2K and LSDIR datasets, our method achieved high PSNR and SSIM scores, indicating that our approach can greatly improve image resolution while preserving image features and textures.

Additionally, when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.
